---
title: "Cancer Distribution in India"
output: 
  flexdashboard::flex_dashboard:
    theme : cerulean
    orientation: columns
    vertical_layout: fill
    social : ["facebook", "twitter", "menu"]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(pivottabler)
```

```{r}

data<-read.csv("D:/All Tutorials Studies/R_TUT/Projects/Data Visualization/CP1.csv")
```


```{r}
mycolors<- c("blue", "#FFC125", "darkgreen", "darkorange")

```


Cancer Patient
================================

Row 
-----------------------------------------------------------------------
### Total Unique States

```{r}
valueBox(length(unique(data$States)),
         icon = "fa-building")

```



### Total Patients in Year 2011 

```{r}

valueBox(sum(data$Y11),
     icon = "fa-user")
```



### Total Patients in Year 2012

```{r}

valueBox(sum(data$Y12),
     icon = "fa-user")
```



### Total Patients in Year 2013

```{r}

valueBox(sum(data$Y13),
     icon = "fa-user")
```



### Total Patients in Year 2014

```{r}

valueBox(sum(data$Y14),
     icon = "fa-user")
```

Row
-----------------------------------------------------------------------


### Patient versus  Indivisual state and Year



```{r}
p1 <- data %>%
         group_by(States) %>%
        summarise(count = n()) %>%
         plot_ly(x = ~States,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Patient By State"),
yaxis = list(title = 'Count'))
p1

```





### Year 2011 COUNT Vs State





```{r}
P2011 <- data %>%
        group_by(States) %>%
        summarise(YS11 = sum(Y11)) %>%
         plot_ly(x = ~States,
                 y = ~YS11,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Patient By State"),
yaxis = list(title = 'Count'))

P2011 

```




### Year 2012 COUNT Vs State

```{r}
P2012 <- data %>%
        group_by(States) %>%
        summarise(YS12 = sum(Y12)) %>%
         plot_ly(x = ~States,
                 y = ~YS12,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Patient By State"),
yaxis = list(title = 'Count'))

P2012 

```



### Year 2013 COUNT Vs State

```{r}
P2013 <- data %>%
        group_by(States) %>%
        summarise(YS13 = sum(Y13)) %>%
         plot_ly(x = ~States,
                 y = ~YS13,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Patient By State"),
yaxis = list(title = 'Count'))

P2013 

```


### Year 2014 COUNT Vs State

```{r}
P2014 <- data %>%
        group_by(States) %>%
        summarise(YS14 = sum(Y14)) %>%
         plot_ly(x = ~States,
                 y = ~YS14,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Patient By State"),
yaxis = list(title = 'Count'))

P2014 

```



Data Table
==============================================

### Data Table

```{r}
datatable(data,
          caption = "Patient's Data",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```




Pivot Table
======================================

### Pivot Table


```{r}
rpivotTable(data,rows="States", cols=c("Y11"),width="100%", height="400px")

```


About Report {data-orientation=columns} 
===========================================

### About Report 
* This is about Number cancer patient in India.

*The dataset Contains `r length(unique(data$States))` Unique State.

*Total Number of Cancer patient  `r sum(data$Total)` .

